Secure Multi-Party Computation with SCALE-MAMBA

### 2019-04-22 paper.tex
Fertig

\begin{abstract}
This paper examines Secure Multi-Party Computation(SMPC), especially the SCALE-MAMBA protocol. To do that, it first introduces SMPC, afterwards SPDZ, the predecessor of SCALE-MAMBA, and, after taking a detailed look at SCALE-MAMBA, compares them. It focuses on the algorithmic foundations of SCALE-MAMBA, especially the split into online and offline phase, how beaver triples are used to enable computational efficient multiplications and which computational complexities the algorithms posses. Afterwards, it tries to depict the evolution in the different versions of the protocol and to locate SCALE-MAMBA between its competitors. Ultimately, it will show some exemplary implementations in real world applications and will give an outlook what further evolutions might be coming in the next years.
\end{abstract}

\section{Motivation and Introduction}\label{sec:intromoti}
In today's world, and even more in the future, there exist a lot of computations that have to be done in a distributed environment, because in a lot of use cases multiple parties are involved, but also because the amount of data is getting so big that it often becomes impossible to have a single entity that processes and stores all of it. Furthermore, in a lot of these cases the parties participating in these computations do not want to reveal their own information, because it is sensitive or it has a high business value.\\
A basic example is an anonymous voting. In most elections there is a third party that has to aggregate and count the votes. For instance in Germany's elections, this is done by specific persons counting the local votes then forwarding the information to a central institution. The other problem is that it has to be guaranteed that a vote is valid, meaning that each voter holds the right to vote and is only voting one time. So in an ideal system, no person participating in the aggregation process should be able to get any information over any vote or any subset of votersx.\\
Another use case is the exchange of medical data. Medical data of patients is highly confidential and should never be published. But at the same time, a lot of different hospitals or doctors have only the data from their small data set of local patients, and for making founded diagnosis for new patients it would be helpful to compare the symptoms to the diagnoses of other doctors.\\
Secure Multi-Party Computation(SMPC) is one possible solution for these use cases. It is a field of research that emerged within the last 30 years, and is gathering a lot of speed in the last years. 
The basic problem is the evaluation of a common function, to which multiple parties have different inputs, without revealing these inputs. Although there are a lot of theoretical solutions for this problem, real-world implementations are still not performing on the desired level. So in the last years the research shifted more into the area of how to improve the performance of existing solutions while still guaranteeing a desired level of security.\\
This paper's main focus will lay on SCALE-MAMBA, a system developed mainly by the Katholieke Universiteit Leuven. This system is one of the forerunners in SMPC and combines a lot of research by different teams to provide a platform with highly performant SMPC. Nevertheless, this paper will at first give a short introduction into the history of SMPC and will try to explain its basic technologies to the reader. It will compare SCALE-MAMBA to its predecessors and will also try to give a short comparison to other SMPC systems which use different approaches, especially taking a look on which different requirements are fulfilled by each. Ultimately, it will try to give an outlook what might be coming in the next years.\\
\section{SMPC Basics and History}\label{sec:smpc}
\subsection{Beginnings}
As we saw in the introduction, there are a lot current and much more upcoming use cases of calculating the output of a function in a distributed environment with multiple parties while at the same time keeping all the individual inputs secret. The first explorations in these fields started in the 1970s, with theoretical problems like the mental poker problem(how can two players play poker while not being in the same physical location and making sure no one is cheating) and Yao's millionaire problem(how can can two millionaires decide who is richer than the other while not revealing their respective wealth). \\
These explorations lead to a group of basic protocols which established the area of Secure Multi-Party Computation(SMPC).\\
\subsection{Problem statement}
Formally, the SMPC problem can be stated as follows:
\begin{itemize}
\item Given a finite field \( \mathcal{F}_p=\{0,...,p-1\}\) with a prime p
\item Given \(n\) parties \(P_1,...,P_n\) participating in the computation
\item Given \(m\) secret inputs \(x_1,...,x_m\) with each of them hold by one of the parties
\item Given a function \(f(x_1,...,x_m)\)
\item Goal: Evaluation of the function \(f(x_1,...,x_m)\) while guaranteeing secrecy and correctness
\end{itemize}
\textbf{Secrecy:} If party \(P_i\) holds secret \(x_j\), then at the end of the evaluation no information regarding \(x_j\) is revealed to the other parties.\\
\textbf{Correctness:} At the end of the computation, the result is correct.\\\\
In a lot of cases each party has exactly one corresponding secret input, but this is not necessarily required. There can also be parties without input and parties with multiple inputs.\\
Now we will take a short look on two of the first protocols, which both are the basis for a whole family of SMPC schemes.
\subsection{Yao's Garbled Circuit}
There are typically two families, into which most of the SMPC protocols can be categorized. One is based on garbled circuits which were first introduced by Yao in 1986 \cite{4568207}. The basic idea is that, in a two party setting, one party, Alice, garbles the Boolean circuit that has to be evaluated and sends it to the second party, Bob. Bob uses his own input, Alice's encrypted input and the garbled circuit to evaluate the circuit in an encrypted way. At the end they exchange the results and can compute the result this way. 
\subsection{Shamirs Secret Sharing Scheme}
This paper will not further discuss the family of garbled circuit protocols, but rather the second family which are protocols based on so called Linear Secret Sharing. 
These type of protocols were introduced by Adi Shamir at a similar time, in 1979 \cite{Shamir:1979:SS:359168.359176}.\\
The basic idea of this approach is the the so called share-compute-reveal paradigm, which splits the evaluation of the function into three parts.\\
\textbf{Share:} First, the inputs secrets are split into multiple parts which then are shared shared with the other parties. Hence, every party holds a share of each input secret.\\
\textbf{Compute:} The parties evaluate the function with the secret input shares. The protocol has to be defined in a way, that the final result which each parties computes with the input shares is a respective share of the complete final resut.\\
\textbf{Reveal:} The parties agregate their shares of the final result and compute the final result together.\\
This paradigm already shows a lot of challenges arising for a concrete protocol, for instance:
\begin{itemize}
\item How can the secrets be shared in a homomorphic way, so that, after computing on shared input, the complete result can be recovered from the result shares?
\item While this can be done for addition in easy ways, how can this be done for multiplication as well?
\item How can the correctness of the computation be verified?
\item How can the overhead generated by a protocol can be kept in a reasonable size, so that a protocol is applicable to a real-world use case?
\end{itemize}
In Shamir's scheme the secret sharing is implemented by expressing a secret $s$ and its shares as a random polynomial $f(x)$, so that $f(0)=s$ and each share $s_i$ has the value $s_i=f(i)$. Computations are executed on these shares, and at the end it is possible to reconstruct the result from the different shares without revealing information about the initial secrets. This is done by using Lagrange interpolation. . The degree $p$ of the polynomial can be seen as a security parameter, because $p$ shares are needed to reconstruct the secret.\\
There is a huge family of protocols build on this approach, and it is still evolving every day. This paper will focus on the newest of these protocols that were developed in the last 10 years, especially on the protocols which are based on or similar to SPDZ. \\
Before looking into exact implementations of linear secret sharing schemes, following, a short look will taken at the general adversary model and required basic definitions.
\subsection{Adversary Model}
In cryptography, the adversary which is considered is normally a third party that wants to get information for his own gain or want to sabotage something because of his own interest. In SMPC it is expected that the adversary is not only participating as one party, but could could control multiple parties. That means a potential adversary can control between one and all but one of the parties which are participating. The difference to the normal cryptographic adversary model is, that the adversary is controlling parties that are participating in the scheme and not a third party that tries to intercept communication.\\
In the area of SMPC there is normally a differentiation between two types of adversaries.
\subsubsection{Honest but curious}
The honest but curious adversary tries to gain as much information as possible while obeying the rules of the protocol. Hence, it is impossible to know that this party is controlled by a third entity. This adversary tries to retrieve some of the secret information from the other parties, by using all the information he gets during the execution of the protocol.
\subsubsection{Malicious adversary}
While this adversary also wants to gain all the information, he is not obeying the rules of the protocol. This type of adversary can send different inputs to manipulate the results he receives. Furthermore, he wants to interrupt the whole protocol. That could mean making the computation impossible, but as well modifying his own input or his own calculations, so the final result is changed and might lead to different implications
It is important to distinguish between these two types of adversary, because it shows the different securities SMPC has to guarantee. It has to guarantee that no information is unwillingly shared with an illegal party and at the same time verify that the final result has a correct value. Most SMPC protocols try to guarantee safety versus both type of adveraries, bvut there are also approaches that only use passive security, i.e. only protecting versus non malicious adversaries.
\subsection{Access structures}
There are a lot of different use cases for SMPC, so of course the adversary model changes depending on the system, the security needs, and the amount of parties involved. it is important to differentiate between these different use cases, because the different needs have big implications for security measurements that have to be taken and, thus, for runtime complexity. SMPC should run as fast as possible, while still providing all the necessary security guarantees.\\
To describe which party has which rights, and how many parties can be corrupted, so that the security can still be guaranteed, access structures were introduced.
An access structure describes how many parties are needed to form a so called qualified set. A qualified set is a group of parties which can pool their information to extract secret information. An access structure is called \(Q_l \)-access structure if at least \(l+1\) parties are needed to  form a qualified set. 
An \((n,t)\)-threshold scheme with \(t<\frac{n}{l}\) means that at least \(t+1\) parties are needed to form a qualified set. Here, \(n\) is the number of total parties, and \(t\) is the number of possible adversaries while not revealing any secrets ~\cite{MPCBook_threshold}.\\

@@

An access structure also does not have to be symmetric. In some cases there might be different type of parties, where different parties have different positions or levels of trust, so it is, for example, possible to specify that some set of parties only has to have the size of 2 to form a qualified set and another one needs the size of 4.\\
Choosing the right access structure for the right use case is important, because it has a big impact on performance and on the desired security level.

\section{SCALE-MAMBA}\label{sec:scalemamba}

\subsection{Overview}

In the last years, research in SMPC is constantly ongoing, and there are new approaches and improvements to old approaches appearing regularly. But most of these publications only focus on a small area of the whole picture. SCALE-MAMBA\cite{ScaleMambaDocu} is a project that tries to combine the state-of-the-art research into one system. That means that it is offering an end-to-end system for SMPC.\\
It is a research system that is continuously in development, therefore, there is not a single final version that can be examined. It offers a wide range of protocols for different use cases, i.e. it is possible to use the system in different configurations. That also means for this paper, that there is not a single protocol that can be examined. Thus, this paper tries to give more of an overview how the process works in general, which are the main, especially newest and best performing, components and where are the problems and bottlenecks.\\ 
SCALE-MAMBA consists of two parts. One part is called Secure Computation Algorithms from LEuven (SCALE) and is the SMPC part. It contains all the computational logic and algorithms for multi-party computations. The second part is called Multiparty AlgorithMs Basic Argot (MAMBA) and is a compiler for the SMPC programs.

In general, the SCALE protocol is split in two parts, first an offline phase and afterwards an online phase. In the online phase only the final evaluation of the function is executed. In the offline phase, prior to the online phase, preparations are done by all parties to prepare for the evaluation. This already includes calculating values for possible multiplications and MACs, so that the online phase can be executed faster. In this phase the expensive calculations are done, like public key cryptography or authentications, so that the online phase only needs basic primitives. The offline phase is not completely offline, because the parties still exchange some information which are later needed for the evaluation. But this phase is not that time critically, that means it can be already executed a lot earlier than the online phase, so that, when the function evaluation is really needed, the result can be calculated in a rather fast time compared to a system that still has to set up everything. In SCALE-MAMBA, compared to its predecessors, the offline and online phase are completely integrated. Therefore, it is not possible anymore to execute them separately like in SPDZ for example. But it is a much closer approach to a real world application.\\

While SCALE-MAMBA also offers different access structures, the most commonly used security configuration is active security with abort in a full threshold scheme, that means that every party except one could be corrupted, and still no information is leaked, because the evaluation is aborted.

\subsection{MAMBA}
For this paper the most interesting part is the algorithmic. But still, the importance of the compiler should not be undervalued. Although the algorithmic foundations might be more important from a theoretical point of view, the compiler, written in C++, enables the user to use these technologies in a system where he can rely on the security guarantees given by the algorithms. The programs can be written for MAMBA in a syntax similar to python's. In these programs, the user can specify which security settings he wishes to use. He can specify, how he wants his SMPC to exactly be executed, and which security parameters he wants to use. MAMBA compiles the instructions to bytecode which is then executed by SCALE. MAMBA is the part that gives the system the possibility to be properly used and tested. It makes it easy to change the parameters, to execute comparable tests, and to have an abstraction level for the user.\\

\subsection{Secret sharing}
\label{sharing}

As mentioned before, SCALE-MAMBA, and in general similiar protocols like SPDZ, use linear secret sharing.\\
Given party \(P_i\) which holds a secret value \( a \in \mathcal{F}_p\) and a share of the global MAC key \( \alpha\). Then \( P_i\) can additvely share \( a\) with the other \(n-1\) parties as follows:
\begin{enumerate}
\item Choose random \(\delta_a \in \mathcal{F}_p\)
\item Compute tag $ \gamma (a)= \alpha(a+\delta)$
\item Choose random \(a_1,...,a_n \in \mathcal{F}_p\) so that $ a=(a_1+...+a_n)$
\item Choose random \((\gamma (a)_1+...+\gamma (a)_n) \in \mathcal{F}_p\) so that $\gamma (a)=((\gamma (a)_1+...+\gamma (a)_n))$
\item Send  \( \delta_a \) and the respective shares \(a_j \) and \( \gamma (a)_j \) to each party \( P_j \) 
\item Now each party \( P_j\) holds a share of \( a\) as tuple \(\langle a_j\rangle = (\delta_a,a_j,\gamma(a)_j )\)
\end{enumerate}

Now the value of \(a\) and the corresponding tag \(\gamma(a)\) can only be reconstructed if, and only if, all \(n\) secret shares are known. At the same time, no bit of information regarding \(a\) is revealed, as long as not all secret shares are known.\\
\textbf{Correctness:} Assume that $n-1$ secret shares are known to an adversary, i.e. all secret shares except one $a_x \in \mathcal{F}_p $. Then the adversary can calculate $\sum_{i \neq x} a_i = a-a_x$. Nevertheless, because $a_x$ was drawn from an independent distribution and the adversary has no information over the value of \(a_x\), knowing $a-a_x$ reveals not a single bit of information about $a$.\\

\subsection{Revealing secrets}

For obvious reasons, the secrets also have to be revealed again. SCALE-MAMBA uses two different types of revealing them.\\

\textbf{Partial Reveal}
All players send their respective shares of a value, but not the tag share, to one chosen party \(P_i\) which sums up all values and then broadcasts the result. The tag stays secretly shared between the parties.\\
In praxis, the party computing the value is changing for every reveal to keep the workload balanced.\\
\textbf{Full Reveal}
In this case all players broadcast their respective shares and the respective MACs to all players, so all players can calculate the secret and verify the result with the corresponding tag.\\

\subsection{Offline phase}

There are two main things done in the offline phase. The first one is the generation of a global Message Authentication Code(MAC) key $\alpha$. This MAC key is used later, to authenticate the different shares at the end of the computation.\\
The second and and most important part in the offline phase, is the generation of the beaver triples. These triples  are independent of the computation that is later performed in the online phase, but are used in the online phase to express multiplications as a combination of additions and multiplications with constants. For each multiplication, one of the triples is needed.

\subsubsection{Generation of the MAC key}
Message Authentification Codes (MACs) are used to guarantee the integrity and authenticity of a message. Basically, a MAC is a key that is used to generate a tag for a message. This tag is used to verify the identity of the sender and that the content of the message was not changed.\\
For using MACs we need a tupel of two algorithms \((\text{MAC},\text{VER})\):\\
\begin{itemize}
\item The MAC algorithm \(\text{MAC}(K,m)\rightarrow t\) takes a key \(K\) and a message \(m\) and outputs a tag \(t\)\\
\item The verficiation algorithm \(\text{VER}(K,m,t)\rightarrow 0/1\) takes a key \(K\), a message \(m\) and a tag \(t\) and outputs accept(\(1\)) if the tag is correct or reject(\(0\))\\ if it is not
\end{itemize}

In SCALE-MAMBA really simple MACs are used. We assume that we have a MAC key \( \alpha \). Then the MAC algorithm used is following:\\
$$\text{MAC}(\alpha,m)\rightarrow \alpha * m$$ 
$$\text{VER}(\alpha,m,t)\rightarrow (1 \Leftrightarrow t = \alpha*m) $$

This algorithm has the disadvantage of high storage complexity because the tag has the same size as the message, which is a difference to other MAC algorithms. But it is symmetric so the same key can be used for creating the tag and verifying it. The symmetry is used for an advantage later on in the protocol.\\

The MAC key is distributively generated, i.e. only if all parties pool together their shares they can recover its value. 
[TODO Expand on MAC generation

\subsubsection{Beaver Triples}

Beaver triples are triples of three numbers \((a,b,c)\), with \( a,b,c\in \mathcal{F}_p \), with \(a\) and \(b\) being chosen uniformly randomly, and \(a*b=c\).
In the offline or pre-processing phase, the most important part is the generation of the beaver triples. These triples  are independent of the computation that is later performed in the online phase, but will be used in the online phase to guarantee that multiplications can be done without revealing the secret inputs of the different parties.\\

For each multiplication operation in the online phase, we need one of the Beaver triples \( (\langle x_1 \rangle ,\langle y_1\rangle , \langle z_1\rangle )\) generated in the offline phase. In the offline phase we checked the quality of our triples, but we still allowed the possibility that each triple has an error \(e\) so that \(c=a*b+e\). To check the quality of our triple, we use a second triple \( (\langle x_2 \rangle ,\langle y_2\rangle ,\langle z_2\rangle )\) in a procedure called sacrificing it. Both triples are additively shared between all parties like the input values. In SPDZ both triples are completely unrelated to each other, and the sacrificing is done as follows:\\

For the generation of a beaver triple $(a,b,c)$, homomorphic public key cryptography based on the Brakerski-Gentry-Vaikuntanathan encryption scheme~\cite{cryptoeprint:2011:277} is used. Every party $P_i$ generates for the communication with each party $P_j$ a set of keys $(pk_{ij},sk_{ij})$. Then, one triple is generated as follows:

>>>>

\begin{abstract}
This paper examines Secure Multi-Party Computation (SMPC), especially the SCALE-MAMBA protocol. First it introduces Secure Multi-Party Computation and fundamental primitives, and then takes a detailed look at SCALE-MAMBA, especially in comparison to its predecessor SPDZ. It focuses on the algorithmic foundations, especially the split into online and offline phase, how beaver triples are used to enable computational efficient multiplications and which computational complexities the algorithms posses. Afterwards, it tries to depict the evolution in the different versions of the protocol and tries to locate SCALE-MAMBA between its competitors. Ultimately, it will show some exemplary implementations in real world applications and will give an outlook what further evolutions might be coming in the next years.
\end{abstract}

\section{Motivation and Introduction}\label{sec:intromoti}
In today's world, and even more in the future, there exist a lot of computations that have to be done in a distributed environment, because in a lot of use cases multiple parties are involved, but also because the amount of data is getting so big that it often becomes impossible to have a single entity that processes and stores all of it. Furthermore, in a lot of these cases the parties participating in these computations do not want to reveal their own information, because it is sensitive or it has a high business value.

A basic example is an anonymous voting. In most elections there is a third party that has to aggregate and count the votes. For instance in Germany's elections, this is done by specific persons counting the local votes then forwarding the information to a central institution. The other problem is that it has to be guaranteed that a vote is valid, meaning that each voter holds the right to vote and is only voting one time. So in an ideal system, no person participating in the aggregation process should be able to get any information over any vote or any subset of voters.

Another use case is the exchange of medical data. Medical data of patients is highly confidential and should never be published. But at the same time, a lot of different hospitals or doctors have only the data from their small data set of local patients, and for making founded diagnosis for new patients it would be helpful to compare the symptoms to the diagnoses of other doctors.

Secure Multi-Party Computation (SMPC) is one possible solution for these use cases, because we can model above mentioned and a lot similar problems as functions. SMPC is a field of research that emerged within the last 30 years, and is gathering a lot of speed in the last years. 
The basic problem is the evaluation of a common function, to which multiple parties have different inputs, without revealing these inputs. Although there are a lot of theoretical solutions for this problem, real-world implementations are still not performing on the desired level. So in the last years the research shifted more into the area of how to improve the performance of existing solutions while still guaranteeing a desired level of security.

This paper's main focus will lay on SCALE-MAMBA~\cite{ScaleMambaDocu}, a system developed mainly by the Katholieke Universiteit Leuven. This system is one of the forerunners in this area and combines a lot of research by different teams to provide a platform with highly performant SMPC. Nevertheless, this paper will at first give a short introduction into the history of SMPC and will try to explain its basic technologies to the reader. It will compare SCALE-MAMBA to its predecessors and will also try to give a short comparison to other SMPC systems which use different approaches, especially taking a look on which different requirements are fulfilled by each. Ultimately, it will try to give an outlook what might be coming in the next years.
\section{SMPC Basics and History}\label{sec:smpc}
\subsection{Beginnings}
As we saw in the introduction, there are a lot current, and much more upcoming, use cases of calculating the output of a function in a distributed environment with multiple parties while at the same time keeping all the individual inputs secret. The first explorations in these fields started in the 1970s, with theoretical problems like the mental poker problem~\cite{mentalPoker}, that asks how two players can play poker while not being in the same physical location and making sure no one is cheating, and Yao's millionaire problem~\cite{Yao1982ProtocolsFS}, which tries to answer the question which of two millionaires is richer than the other while not revealing their respective wealth.

These explorations led to a group of basic protocols which established the area of Secure Multi-Party Computation(SMPC).\\
\subsection{Problem statement}
Formally, the SMPC problem can be stated as follows:
\begin{itemize}
\item Given a finite field \( \mathcal{F}_p=\{0,...,p-1\}\) with a prime p
\item Given \(n\) parties \(P_1,...,P_n\) participating in the computation
\item Given \(m\) secret inputs \(x_1,...,x_m\) with each of them hold by one of the parties
\item Given a function \(f(x_1,...,x_m)\)
\item Goal: Evaluation of the function \(f(x_1,...,x_m)\) while guaranteeing secrecy and correctness
\end{itemize}
\textbf{Secrecy:} If party \(P_i\) holds secret \(x_j\), then at the end of the evaluation no information regarding \(x_j\) is revealed to the other parties.\\
\textbf{Correctness:} At the end of the computation, the result is correct.\\\\
In a lot of cases each party has exactly one corresponding secret input, but this is not necessarily required. There can also be parties without input and parties with multiple inputs.

Now we will take a short look on two of the first protocols, which both are the basis for a whole family of SMPC schemes.
\subsection{Yao's Garbled Circuit}
There are typically two families, into which most of the SMPC protocols can be categorized. One is based on garbled circuits which were first introduced by Yao in 1986~\cite{4568207}. The basic idea is that, in a two party setting, one party, Alice, encrypts the Boolean circuit that has to be evaluated and sends it to the second party, Bob. Bob uses his own input, Alice's encrypted input and the garbled circuit to evaluate the circuit in an encrypted way. At the end they exchange the results and can compute the result this way. 
\subsection{Shamirs Secret Sharing Scheme}
This paper will not further discuss the family of garbled circuit protocols, but rather the second family, which are protocols based on so called Linear Secret Sharing. 
These type of protocols were introduced by Adi Shamir at a similar time, in 1979~\cite{Shamir:1979:SS:359168.359176}.

The basic idea of this approach is the the so called share-compute-reveal paradigm, which splits the evaluation of the function into three parts.\\\\
\textbf{Share:} First, the inputs secrets are split into multiple parts which then are shared with the other parties. Hence, every party holds a share of each input secret.\\
\textbf{Compute:} The parties evaluate the function with the secret input shares. The protocol has to be defined in a way, that the final result which each parties computes with the input shares is a respective share of the complete final result.\\
\textbf{Reveal:} The parties aggregate their shares of the final result and compute the final result together.

This paradigm already shows a lot of challenges arising for a concrete protocol, for instance:
\begin{itemize}
\item How can the secrets be shared in a homomorphic way, so that, after computing on shared inputs, the complete result can be recovered from the result shares?
\item While this can be done for addition in easy ways, how can this be done for multiplication as well?
\item How can the correctness of the computation be verified?
\item How can the overhead generated by a protocol can be kept on a reasonable scale, so that a protocol is applicable to a real-world use case?
\end{itemize}
In Shamir's scheme the secret sharing is implemented by expressing a secret $s$ and its shares as a random polynomial $f(x)$, so that $f(0)=s$ and each share $s_i$ has the value $s_i=f(i)$. Computations are executed on these shares, and at the end it is possible to reconstruct the result from the different shares without revealing information about the initial secrets. This is done by using Lagrange interpolation. The degree $p$ of the polynomial can be seen as a security parameter, because $p+1$ shares are needed to reconstruct the secret.

There is a huge family of protocols build on this approach, and it is still evolving every day. This paper will focus on the newest of these protocols that were developed in the last 10 years, especially on the protocols which are based on or similar to SPDZ~\cite{cryptoeprint:2011:535} which was published in 2011.

Before looking into exact implementations of linear secret sharing schemes, following, a short look will taken at the general adversary model and required basic definitions.
\subsection{Adversary Model}
In cryptography, the adversary which is considered is normally a third party that wants to get information for his own gain or want to sabotage a protocol because of his own interest. In SMPC it is expected that the adversary is not only participating as one party, but could control multiple parties. That means a potential adversary can control between one and all but one of the parties which are participating. The difference to the normal cryptographic adversary model is, that the adversary is controlling parties that are participating in the scheme and not a third party that tries to intercept communication.

In the area of SMPC there is normally a differentiation between two types of adversaries.
\subsubsection{Honest-but-curious}
The honest-but-curious adversary tries to gain as much information as possible while obeying the rules of the protocol. Hence, it is impossible to know that this party is controlled by a third entity. This adversary tries to retrieve some of the secret information from the other parties, by using all the information he gets during the execution of the protocol.
\subsubsection{Malicious adversary}
While this adversary also wants to gain all possible information, he is not obeying the rules of the protocol. This type of adversary can send different inputs to manipulate the results he receives. Furthermore, he wants to interrupt the whole protocol. That could mean making the computation impossible, but as well modifying his own input or his own calculations, so the final result is changed and might lead to different implications.

It is important to distinguish between these two types of adversary, because different measures are needed for each adversary. Additionally, some protocols only provide passive security, which means they protect against a honest-but-curious adversary but not against a malicious one.
\subsection{Access structures}
There are a lot of different use cases for SMPC, so of course the adversary model changes depending on the system, the security needs, and the amount of parties involved. It is important to differentiate between these different use cases, because the different needs have big implications for security measures that have to be taken and, thus, for run-time complexity. SMPC should run as fast as possible, while still providing all the necessary security guarantees.

To describe which party has which rights, and how many parties can be corrupted, so that the security can still be guaranteed, access structures were introduced.
An access structure describes how many parties are needed to form a so called qualified set. A qualified set is a group of parties which can pool their information to extract secret information. An access structure is called \(Q_l \)-access structure if at least \(l+1\) parties are needed to  form a qualified set. 
An \((n,t)\)-threshold scheme with \(t<\frac{n}{l}\) means that at least \(t+1\) parties are needed to form a qualified set~\cite{MPCBook_threshold}. Here, \(n\) is the number of total parties, and \(t\) is the number of possible adversaries while not revealing any secrets.

@@

An access structure also does not have to be symmetric. In some cases there might be different type of parties, where different parties have different positions or levels of trust, so it is, for example, possible to specify that some set of parties only has to have the size of 2 to form a qualified set and another one needs the size of 4.

Choosing the right access structure for the right use case is important, because it has a big impact on performance and on the desired security level.
\section{SCALE-MAMBA}
\label{sec:scalemamba}
\subsection{Overview}
In the last years, research in SMPC is constantly ongoing, and there are new approaches and improvements to old approaches appearing regularly. But most of these publications only focus on a small area of the whole picture. SPDZ~\cite{cryptoeprint:2011:535} is a system that appeared in 2011 and, with a lot of evolutions, was one of the most refined SMPC schemes.

SCALE-MAMBA\cite{ScaleMambaDocu} is the newest successor of SPDZ and is a project that tries to combine most of the state-of-the-art research into one system. This implies that it is offering an end-to-end system for SMPC.

It is a research system that is continuously in development, therefore, there is not a single final version that can be examined. It offers a wide range of protocols for different use cases, i.e. it is possible to use the system in different configurations. That also means for this paper, that there is not a single protocol that can be examined. Thus, this paper tries to give more of a overview how the process works in general, which are the main, especially newest and best performing, components and where are the problems and bottlenecks. This overview is only selective and by no means complete.

SCALE-MAMBA consists of two parts. One part is called Secure Computation Algorithms from LEuven (SCALE) and is the SMPC part. It contains all the computational logic and algorithms for multi-party computations. The second part is called Multiparty AlgorithMs Basic Argot (MAMBA) and is a compiler for the SMPC programs.

In general, the SCALE protocol is split in two parts, first an offline phase and afterwards an online phase. In the online phase only the final evaluation of the function is executed. In the offline phase, prior to the online phase, preparations are done by all parties to prepare for the evaluation. This already includes calculating values for possible multiplications and message authentication codes, so that the online phase can be executed faster. In the offline phase the expensive calculations are done, like public key cryptography or authentications, so that the online phase only needs basic primitives. The offline phase is not completely offline, because the parties still exchange some information which are later needed for the evaluation. But this phase is not that time critically, that means it can be already executed a lot earlier than the online phase, so that, when the function evaluation is really needed, the result can be calculated in a rather fast time compared to a system that still has to set up everything. In SCALE-MAMBA, compared to its predecessors, the offline and online phase are completely integrated. Therefore, it is not possible anymore to execute them separately like it was in SPDZ for example. This is done to be closer to a real-world implementation.

While SCALE-MAMBA also offers different access structures, the most commonly used security configuration is active security with abort in a full threshold scheme, that means that every party except one could be corrupted, and still no information is leaked, because the evaluation is aborted.
\subsection{MAMBA}
For this paper the most interesting part is the algorithmic. But still, the importance of the compiler should not be undervalued. Although the algorithmic foundations might be more important from a theoretical point of view, the compiler, written in C++, enables the user to use these technologies in a system where he can rely on the security guarantees given by the algorithms. The programs can be written for MAMBA in a syntax similar to python's. In these programs, the user can specify which security settings he wishes to use. He can specify, how he wants his SMPC to exactly be executed, and which security parameters he wants to use. MAMBA compiles the instructions to bytecode which is then executed by SCALE. Because of MAMBA, it is much more easy to test and compare different configurations. This abstraction layer makes the system more usable and analyzable.
\subsection{Secret sharing}
\label{sharing}
As mentioned before, SCALE-MAMBA and similar protocols implement the share-compute-reveal paradigm. The sharing is implemented as follows:

Given a party \(P_i\) which holds a secret value \( a \in \mathcal{F}_p\) and a share of the global MAC key \( \alpha\). Then \( P_i\) can additvely share \( a\) with the other \(n-1\) parties as follows:
\begin{enumerate}
\item Choose random \(\delta_a \in \mathcal{F}_p\)
\item Compute tag $ \gamma (a)= \alpha(a+\delta)$
\item Choose random \(a_1,...,a_n \in \mathcal{F}_p\) so that $ a=(a_1+...+a_n)$
\item Choose random \((\gamma (a)_1+...+\gamma (a)_n) \in \mathcal{F}_p\) so that $\gamma (a)=((\gamma (a)_1+...+\gamma (a)_n))$
\item Send  \( \delta_a \) and the respective shares \(a_j \) and \( \gamma (a)_j \) to each party \( P_j \) 
\item Now each party \( P_j\) holds a share of \( a\) as tuple \(\langle a_j\rangle = (\delta_a,a_j,\gamma(a)_j )\)
\end{enumerate}
Now the value of \(a\) and the corresponding tag \(\gamma(a)\) can only be reconstructed if, and only if, all \(n\) secret shares are known. At the same time, no bit of information regarding \(a\) is revealed, as long as not all secret shares are known.\\
\textbf{Correctness:} Assume that $n-1$ secret shares are known to an adversary, i.e. all secret shares except one $a_x \in \mathcal{F}_p $. Then the adversary can calculate $\sum_{i \neq x} a_i = a-a_x$. Nevertheless, because $a_x$ was drawn from an independent distribution and the adversary has no information over the value of \(a_x\), knowing $a-a_x$ reveals not a single bit of information about $a$.\\
\subsection{Revealing secrets}
SCALE-MAMBA uses two different types of revealing a secretly shared value.\\\\
\textbf{Partial Reveal}
All players send their respective shares of a value, but not the tag share, to one chosen party \(P_i\) which sums up all values and then broadcasts the result. The tag stays secretly shared between the parties.\\
In praxis, the party computing the value is changing for every reveal to keep the workload balanced.\\
\textbf{Full Reveal}
In this case all players broadcast their respective shares and the respective MACs to all players, so all players can calculate the secret and verify the result with the corresponding tag.
\subsection{Offline phase}
The offline phase prepares everything, so the function can be evaluated as efficient as possible in the online phase. There are two main things done in the offline phase. The first one is the generation of a global Message Authentication Code(MAC) key $\alpha$. This MAC key is used later, to authenticate the different shares at the end of the computation.

The second and and most important part in the offline phase, is the generation of the beaver triples~\cite{10.1007/3-540-46766-1_34}. These triples are needed in the online phase to express multiplications as a combination of additions and multiplications with constants. For each multiplication, one of the triples is needed.
\subsubsection{Generation of the MAC key}
Message Authentification Codes (MACs) are used to guarantee the integrity and authenticity of a message. Basically, a MAC is a key that is used to generate a tag for a message. This tag is used to verify the identity of the sender and that the content of the message was not changed.\\
For using MACs we need a tupel of two algorithms \((\text{MAC},\text{VER})\):\\
\begin{enumerate}
\item The MAC algorithm \(\text{MAC}(K,m)\rightarrow t\) takes a key \(K\) and a message \(m\) and outputs a tag \(t\)\\
\item The verficiation algorithm \(\text{VER}(K,m,t)\rightarrow 0/1\) takes a key \(K\), a message \(m\) and a tag \(t\) and outputs accept(\(1\)) if the tag is correct or reject(\(0\))\\ if it is not
\end{enumerate}
In SCALE-MAMBA really simple MACs are used. We assume that we have a MAC key \( \alpha \). Then the MAC algorithm used is following:\\
$$\text{MAC}(\alpha,m)\rightarrow \alpha * m$$ 
$$\text{VER}(\alpha,m,t)\rightarrow (1 \Leftrightarrow t = \alpha*m) $$ 
Compared to other MAC algorithms, this algorithm has high storage complexity because the tag has the same size as the message. But it has other advantages, which are that it is not computation complex with only one multiplication, it is symmetric and it is homomorphic.

The MAC key is distributively generated, so that every party has a additive share $\alpha_i$. Only at the end of the computation, the parties aggregate their shares to verify the result.
\subsubsection{Beaver Triples}
Beaver triples, introduced in~\cite{10.1007/3-540-46766-1_34}, are triples of three numbers \((a,b,c)\), with \( a,b,c\in \mathcal{F}_p \), with \(a\) and \(b\) being chosen uniformly randomly, and \(a*b=c\).
In the offline or pre-processing phase, the most important part is the generation of the beaver triples. These triples  are independent of the computation that is later performed in the online phase, but will be used in it to guarantee that multiplications can be done without revealing the secret inputs of the different parties.

For each multiplication operation in the online phase, we need one of the Beaver triples \( (\langle x_1 \rangle ,\langle y_1\rangle , \langle z_1\rangle )\) generated in the offline phase. In the offline phase we checked the quality of our triples, but we still allowed the possibility that each triple has an error \(e\) so that \(c=a*b+e\). To check the quality of our triple, we use a second triple \( (\langle x_2 \rangle ,\langle y_2\rangle ,\langle z_2\rangle )\) in a procedure called sacrificing it. Both triples are additively shared between all parties like the input values. In SPDZ both triples are completely unrelated to each other, and the sacrificing is done as follows:
